Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-30 thesis/acm/paper.tex
Changed author blocks + categories/keywords

\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}

\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective
\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as \textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}

@@

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

>>>>

\conferenceinfo{14th International Workshop on Principles of Software Evolution}{2015 Bergamo, Italy}

\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
\subtitle{[Extended Abstract]
}

@@

\terms{Theory, Design or Verification maybe?}

\keywords{API Design, Software Evolution, Software Maintenance}
